Demystifying the Computer Science Ph.D. Admission in the US \\{\Large A guide for Vietnamese and International Students

### 2023-06-11 phd-cs-us.tex
updates

\newcommand{\mycomment}[3][\color{black}]{{#1{{#2}: {#3}}}}
\newcommand{\tvn}[1]{\mycomment{TVN}{#1}}{}
\newcommand{\tl}[1]{\mycomment{ThanhLe}{#1}}{}
\newcommand{\red}[1]{{\color{red}{#1}}}
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Tab.}
\title{Demystifying the Computer Science Ph.D. Admission in the US \\{\Large A guide for Vietnamese and International Students}}
\date{\today}
\author{\small ThanhVu (Vu) Nguyen, George Mason University}
%\setcounter{secnumdepth}{3}
\begin{document}
\maketitle

@@

If you have suggestions or comments, feel free to create a \href{https://github.com/nguyenthanhvuh/phd-cs-us/issues}{GitHub issue} for discussion.
\end{abstract}

@@

\begin{commentbox}
Vu: One of the reasons I create this post is that several of my colleagues are interested in 
recruiting Vietnamese students and were surprised when seeing very few applications in Vietnam (e.g., our CS PhD program has on average 3 applications from Vietnam each year). In general the number of
PhD applications from Vietnam to US universities is very low and  more would be very welcomed. 
\end{commentbox}

@@

\begin{commentbox}
Vu: Vietnamese students often mention Scopus Q1, which consists of diverse journals from IEEE, Elsevier, and many other publishers unfamiliar to me.  Honestly, I don't know/recognize many of journals listed in Scopus Q1 and. So this might be something to be mindful of, as \textbf{CS} faculty might not be too familiar with Scopus or journals listed in there, so devote sometime in your statement to discuss the significance of your papers.
\end{commentbox}

@@

\begin{commentbox}
Vu: In Vietnam some letter writers ask the applicants to write their own letters so they can just sign. As mentioned, this will hurt the applicants (admission committee are actually quite good at determining this)! I was told that some people did this to ensure the applicants will only go to places where they want to the students to go to (e.g., stay in Vietnam or go to specific places where they have networks). 
\end{commentbox}

\begin{commentbox}
Vu: Vietnamese students sometimes go through great length just to get letters from well-known senior professors in their school, but the letters are generic and carry little value, in fact, \red{red flags}. Moreover, a top professor in Vietnamese might not be well-known to US faculty (see more details in \S\ref{sec:your-school}). So save the trouble and just get letters from \emph{any} professors/supervisors who knows you well and can write a good letter about your research ability.

@@

Many people have contributed to this document.
Craig Yu (GMU) and Hakan Aydin (GMU) provided valuable input in the early version. Other GMU faculty members also have provided feedback and contributions.  Many Vietnamese students have provided feedback and contributed questions, which provide contents for the writing.
\bibliographystyle{abbrv}
\bibliography{phd-cs-us.bib}
\newpage

>>>>

\newcommand{\mycomment}[3][\color{black}]{{#1{{#2}: {#3}}}}
\newcommand{\tvn}[1]{\mycomment{TVN}{#1}}{}
\newcommand{\tl}[1]{\mycomment{ThanhLe}{#1}}{}
\newcommand{\red}[1]{{\color{red}{#1}}}
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Tab.}
\title{Demystifying the Computer Science Ph.D. Admission in the US \\{\Large A guide for Vietnamese and International Students}}
\date{\today}
\author{\small \href{https://nguyenthanhvuh.github.io}{ThanhVu (Vu) Nguyen}, \href{https://cs.gmu.edu}{George Mason University}}
%\setcounter{secnumdepth}{3}
\begin{document}
\maketitle

@@

If you have questions or comments, feel free to create a \href{https://github.com/nguyenthanhvuh/phd-cs-us/issues}{GitHub issue} for discussion.
\end{abstract}

@@

\begin{commentbox}
Vu: One of the reasons I create this post is that several of my colleagues are interested in 
recruiting Vietnamese students and were surprised when seeing very few applications in Vietnam (e.g., our CS PhD program has on average 5-6 applications from Vietnam each year). In general the number of
PhD applications from Vietnam to US universities is few and  more would be very welcomed. 
\end{commentbox}

@@

\begin{commentbox}
Vu: Many international students mention Scopus Q1, which consists of diverse journals from IEEE, Elsevier, and many other publishers unfamiliar to me.  Honestly, I don't know/recognize many of journals listed in Scopus Q1 and. So this might be something to be mindful of, as \textbf{CS} faculty might not be too familiar with Scopus or journals listed in there, so devote sometime in your statement to discuss the significance of your papers.
\end{commentbox}

@@

\begin{commentbox}
Vu: Some letter writers ask the applicants to write their own letters so they can just sign. As mentioned, this will hurt the applicants (admission committee are actually quite good at determining this)! I was told that some people did this to ensure the applicants don't go abraod or only go to places where they want to the students to go to.
\end{commentbox}

\begin{commentbox}
Vu: Sometimes students would go through great length just to get letters from well-known senior professors in their school, but the letters are generic and carry little value, in fact, \red{red flags}. Moreover, a top professor in Vietnam might not be well-known to US faculty (see more details in \S\ref{sec:your-school}). So save the trouble and just get letters from \emph{any} professors/supervisors who knows you well and can write a good letter about your research ability.

@@

Many people have contributed to this document.
Craig Yu (GMU) and Hakan Aydin (GMU) provided valuable input in the early version. Other GMU faculty members also have provided feedback and contributions.  Many students have provided feedback and contributed questions, which provide contents for the writing.
\bibliographystyle{abbrv}
\bibliography{phd-cs-us.bib}
\newpage
